Appendix B

### 2021-10-22 instrument.tex
Appendices

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmainfont[]{Helvetica}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Light Exposure Behavior Assessment (LEBA): Long and Short Form},
  pdfauthor={Mushfiqul Anwar Siraji*, Rafael Robert Lazar*, Juliëtte van Duijnhoven, Luc Schlangen, Shamsul Haque, Vineetha Kalavally, Céline Vetter, Gena Glickman, Karin Smolders, \& Manuel Spitschan**},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{LEBA}
\usepackage{csquotes}
\ifXeTeX
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form}
\author{Mushfiqul Anwar Siraji\textsuperscript{*}, Rafael Robert Lazar\textsuperscript{*}, Juliëtte van Duijnhoven\textsuperscript{}, Luc Schlangen\textsuperscript{}, Shamsul Haque\textsuperscript{}, Vineetha Kalavally\textsuperscript{}, Céline Vetter\textsuperscript{}, Gena Glickman\textsuperscript{}, Karin Smolders\textsuperscript{}, \& Manuel Spitschan\textsuperscript{**}}
\date{}

\affiliation{\vspace{0.5cm}\textsuperscript{*} Joint first authors\\\textsuperscript{**} Corresponding author: \href{mailto:manuel.spitschan@psy.ox.ac.uk}{\nolinkurl{manuel.spitschan@psy.ox.ac.uk}}}

\begin{document}
\maketitle

\textbf{Disclaimer}: This is a non-public version of LEBA (dated \today) and still a work in progress. Please do not distribute!

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
\toprule
Long Form (23 Items) \\
\midrule
\endhead
\textbf{F1: Blue Filter} \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1 hour before attempting to fall asleep. \\
\textbf{F2: Natural Light} \\
I spend 30 minutes or less per day (in total) outside. \\
I spend between 1 and 3 hours per day (in total) outside. \\
I spend between 30 minutes and 1 hour per day (in total) outside. \\
I spend more than 3 hours per day (in total) outside. \\
I spend as much time outside as possible. \\
I go for a walk or exercise outside within 2 hours after waking up. \\
\textbf{F3: Smart Device} \\
I use my mobile phone within 1 hour before attempting to fall asleep. \\
I look at my mobile phone screen immediately after waking up. \\
I check my phone when I wake up at night. \\
I look at my smartwatch within 1 hour before attempting to fall asleep. \\
I look at my smartwatch when I wake up at night. \\
\textbf{F4: Sleep Environment} \\
I dim my mobile phone screen within 1 hour before attempting to fall asleep. \\
I use a blue-filter app on my computer screen within 1 hour before attempting to fall asleep. \\
I use as little light as possible when I get up during the night. \\
I dim my computer screen within 1 hour before attempting to fall asleep. \\
\textbf{F5: Electric Light} \\
I use tunable lights to create a healthy light environment. \\
I use LEDs to create a healthy light environment. \\
I use a desk lamp when I do focused work. \\
I use an alarm with a dawn simulation light. \\
I turn on the lights immediately after waking up. \\
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
\toprule
Short Form (17 Items) \\
\midrule
\endhead
\textbf{F1: Blue Filter} \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1 hour before attempting to fall asleep. \\
\textbf{F2: Natural Light} \\
I spend 30 minutes or less per day (in total) outside. \\
I spend between 1 and 3 hours per day (in total) outside. \\
I spend more than 3 hours per day (in total) outside. \\
I spend as much time outside as possible. \\
I go for a walk or exercise outside within 2 hours after waking up. \\
\textbf{F3: Smart Device} \\
I use my mobile phone within 1 hour before attempting to fall asleep. \\
I look at my mobile phone screen immediately after waking up. \\
I check my phone when I wake up at night. \\
\textbf{F4: Sleep Environment} \\
I dim my mobile phone screen within 1 hour before attempting to fall asleep. \\
I use a blue-filter app on my computer screen within 1 hour before attempting to fall asleep. \\
I dim my computer screen within 1 hour before attempting to fall asleep. \\
\textbf{F5: Electric Light} \\
I use tunable lights to create a healthy light environment. \\
I use LEDs to create a healthy light environment. \\
I use an alarm with a dawn simulation light. \\
\bottomrule
\end{longtable}

\end{document}

>>>>

\clearpage
\makeatletter
\efloat@restorefloats
\makeatother

\begin{appendix}
\section{}
\textbf{Disclaimer}: This is a non-public version of LEBA (dated \today)
and still a work in progress. Please do not distribute!

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
\toprule
Long Form (23 Items) \\
\midrule
\endhead
\textbf{F1: Wearing blue light filters} \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1
hour before attempting to fall asleep. \\
\textbf{F2: Spending time outdoors} \\
I spend 30 minutes or less per day (in total) outside. \\
I spend between 1 and 3 hours per day (in total) outside. \\
I spend between 30 minutes and 1 hour per day (in total) outside. \\
I spend more than 3 hours per day (in total) outside. \\
I spend as much time outside as possible. \\
I go for a walk or exercise outside within 2 hours after waking up. \\
\textbf{F3: Using phone and smartwatch in bed} \\
I use my mobile phone within 1 hour before attempting to fall asleep. \\
I look at my mobile phone screen immediately after waking up. \\
I check my phone when I wake up at night. \\
I look at my smartwatch within 1 hour before attempting to fall
asleep. \\
I look at my smartwatch when I wake up at night. \\
\textbf{F4: Using light before bedtime} \\
I dim my mobile phone screen within 1 hour before attempting to fall
asleep. \\
I use a blue-filter app on my computer screen within 1 hour before
attempting to fall asleep. \\
I use as little light as possible when I get up during the night. \\
I dim my computer screen within 1 hour before attempting to fall
asleep. \\
\textbf{F5: Using light in the morning and during daytime} \\
I use tunable lights to create a healthy light environment. \\
I use LEDs to create a healthy light environment. \\
I use a desk lamp when I do focused work. \\
I use an alarm with a dawn simulation light. \\
I turn on the lights immediately after waking up. \\
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
\toprule
Short Form (17 Items) \\
\midrule
\endhead
\textbf{F1: Wearing blue light filters} \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1
hour before attempting to fall asleep. \\
\textbf{F2: Spending time outdoors} \\
I spend 30 minutes or less per day (in total) outside. \\
I spend between 1 and 3 hours per day (in total) outside. \\
I spend more than 3 hours per day (in total) outside. \\
I spend as much time outside as possible. \\
I go for a walk or exercise outside within 2 hours after waking up. \\
\textbf{F3: Using phone and smartwatch in bed} \\
I use my mobile phone within 1 hour before attempting to fall asleep. \\
I look at my mobile phone screen immediately after waking up. \\
I check my phone when I wake up at night. \\
\textbf{F4: Using light before bedtime} \\
I dim my mobile phone screen within 1 hour before attempting to fall
asleep. \\
I use a blue-filter app on my computer screen within 1 hour before
attempting to fall asleep. \\
I dim my computer screen within 1 hour before attempting to fall
asleep. \\
\textbf{F5: Using light in the morning and during daytime} \\
I use tunable lights to create a healthy light environment. \\
I use LEDs to create a healthy light environment. \\
I use an alarm with a dawn simulation light. \\
\bottomrule
\end{longtable}
\end{appendix}

### 2021-10-22 manuscript.Rmd
Appendices

author: 
  - name          : "Mushfiqul Anwar Siraji"
    affiliation   : "1, *"
    email         : "mushfiqul.anwarsiraji@monash.edu"
    role:         
      - Formal Analysis
      - Visualization
      - Writing – original draft

@@

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    latex_engine: xelatex
mainfont: Helvetica
---

@@

| Name                                            | Authors                     | Description                                                                            | Relevant Items | Adaptations |
|-------------------------------------------------|-----------------------------|----------------------------------------------------------------------------------------|:--------------:|-------------|
| Visual Light Sensitivity Questionnaire-8        | [\@verriotto2017new]        | Eight-question survey to assess the presence and severity of photosensitivity symptoms |      all       | jhghjgjhgfd |
| Office Light Survey                             | [\@eklund1996development]   | Multi-item questionnaire to assess electrical lighting environment in office           |       aa       | gh          |
| Harvard Light Exposure Assessment Questionnaire | [\@bajaj2011validation]     | Self-administered semiquantitative light qestionnaire                                  |       aa       | as          |
| Hospital Lighting Survey                        | [\@dianat2013objective]     | 23 items questionnaire to assess light environment in a hospital                       |       dd       | fg          |
| Morningness-Eveningness Questionnaire           | [\@horne1976self]           | 19 items questionnaire to understand your body clock                                   |       ff       | hj          |
| Munich Chronotype Questionnaire (MCTQ)          | [\@roenneberg2003life]      | 17 items questionnaire to understand individuals phase of entrainment                  |       ff       | jk          |
| Assessment of Sleep Environment                 | [\@grandner2014development] | 13 items questionnaire measuring your sleep environment quality                        |       ff       | kl          |
| The Pittsburgh Sleep Quality Index (PSQI)       | [\@buysse1989pittsburgh]    | 9 items inventory to measure sleep quality and sleeping pattern                        |       ff       | klfrgfgvfg  |
|                                                 |                             |                                                                                        |                |             |
|                                                 |                             |                                                                                        |                |             |

@@

@@

# Plots ####
## F1 Plots ####
F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "Blue Filter OCC")
F1_info <- plot(F1_fit, type = "infoSE", main = "F1")
F1_iteminfo <- plot(F1_fit, type = "infotrace", 
                    facet_items = T, main = "Blue Filter")

## F2 Plots ####
F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "Natural Light OCC")
F2_info <- plot(F2_fit, type = "infoSE", main = "F2")
F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = "Natural Light")

## F3 Plots ####
F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "Smart Device OCC")
F3_info <- plot(F3_fit, type = "infoSE", main = "F3")
F3_iteminfo <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, main = "Smart Device")

## F4 Plots ####
F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "Sleep Environment OCC")
F4_info <- plot(F4_fit, type = "infoSE", main = "F4")
F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "Sleep Environment")

## F5 Plots ####
F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "Electric Light OCC")
F5_info <- plot(F5_fit, type = "infoSE", main = "F5")
F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = "Electric Light")

@@

@@

@@

```{r, results='asis'}
apa_table (theta.correlation.matrix, caption = "correlation coefficents of obtained scores and estimated latent trait for each factots", note = "* p < 0.05; ** p < 0.01; *** p < 0.001"  )
```

>>>>

author: 
  - name          : "Mushfiqul Anwar Siraji"
    affiliation   : "1, *"
    email         : "mushfiqul.anwarsiraji@monash.edu"
    role:         
      - Formal Analysis
      - Visualization
      - Writing – original draft
      - Writing – review & editing;

@@

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    latex_engine: xelatex

mainfont: Helvetica
appendix:
  - "instrument.Rmd"
  - "Appendix-B.Rmd"

---

@@

| Name                                            | Authors                     | Description                                                                            | Relevant Items | Adaptations |

+=================================================+=============================+========================================================================================+:==============:+=============+
| Visual Light Sensitivity Questionnaire-8        | [@verriotto2017new]        | Eight-question survey to assess the presence and severity of photosensitivity symptoms | all            | jhghjgjhgfd |
+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
| Office Light Survey                             | [@eklund1996development]   | Multi-item questionnaire to assess electrical lighting environment in office           | aa             | gh          |
+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
| Harvard Light Exposure Assessment Questionnaire | [@bajaj2011validation]     | Self-administered semiquantitative light qestionnaire                                  | aa             | as          |
+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
| Hospital Lighting Survey                        | [@dianat2013objective]     | 23 items questionnaire to assess light environment in a hospital                       | dd             | fg          |
+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
| Morningness-Eveningness Questionnaire           | [@horne1976self]           | 19 items questionnaire to understand your body clock                                   | ff             | hj          |
+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
| Munich Chronotype Questionnaire (MCTQ)          | [@roenneberg2003life]      | 17 items questionnaire to understand individuals phase of entrainment                  | ff             | jk          |
+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
| Assessment of Sleep Environment                 | [@grandner2014development] | 13 items questionnaire measuring your sleep environment quality                        | ff             | kl          |
+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
| The Pittsburgh Sleep Quality Index (PSQI)       | [@buysse1989pittsburgh]    | 9 items inventory to measure sleep quality and sleeping pattern                        | ff             | klfrgfgvfg  |
+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
=======
|-------------------------------------------------|-----------------------------|----------------------------------------------------------------------------------------|:--------------:|-------------|
| Visual Light Sensitivity Questionnaire-8        | [\@verriotto2017new]        | Eight-question survey to assess the presence and severity of photosensitivity symptoms |      all       | jhghjgjhgfd |
| Office Light Survey                             | [\@eklund1996development]   | Multi-item questionnaire to assess electrical lighting environment in office           |       aa       | gh          |
| Harvard Light Exposure Assessment Questionnaire | [\@bajaj2011validation]     | Self-administered semiquantitative light qestionnaire                                  |       aa       | as          |
| Hospital Lighting Survey                        | [\@dianat2013objective]     | 23 items questionnaire to assess light environment in a hospital                       |       dd       | fg          |
| Morningness-Eveningness Questionnaire           | [\@horne1976self]           | 19 items questionnaire to understand your body clock                                   |       ff       | hj          |
| Munich Chronotype Questionnaire (MCTQ)          | [\@roenneberg2003life]      | 17 items questionnaire to understand individuals phase of entrainment                  |       ff       | jk          |
| Assessment of Sleep Environment                 | [\@grandner2014development] | 13 items questionnaire measuring your sleep environment quality                        |       ff       | kl          |
| The Pittsburgh Sleep Quality Index (PSQI)       | [\@buysse1989pittsburgh]    | 9 items inventory to measure sleep quality and sleeping pattern                        |       ff       | klfrgfgvfg  |

@@

# Model Fit (degrees of freedom too low to check model fit)
#F1.model <- M2(F1_fit)
#F2.model <- M2(F2_fit)
#F3.model <- M2(F3_fit)
#F4.model <- M2(F4_fit)
#F5.model <- M2(F5_fit)

#Item fit
F1.item.fit<- itemfit(F1_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
                                  impute=10)

F2.item.fit<- itemfit(F2_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
                                  impute=10)
F3.item.fit<- itemfit(F3_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
                                  impute=10)
F4.item.fit<- itemfit(F4_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
                                  impute=10)

F5.item.fit<- itemfit(F5_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
                                  impute=10)

#Identigying Missfit items based on RMSEA Value
F1.item_misfits <- subset(F1.item.fit, RMSEA.S_X2 >= .06)
F2.item_misfits <- subset(F2.item.fit, RMSEA.S_X2 >= .06)
F3.item_misfits <- subset(F3.item.fit, RMSEA.S_X2 >= .06)
F4.item_misfits <- subset(F4.item.fit, RMSEA.S_X2 >= .06)
F5.item_misfits <- subset(F5.item.fit, RMSEA.S_X2 >= .06)

@@

# Plots ####
## F1 Plots ####
F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "Blue Filter OCC")
F1_info <- plot(F1_fit, type = "infoSE", main = "F1")
F1_iteminfo <- plot(F1_fit, type = "infotrace", 
                    facet_items = T, main = "F1")

## F2 Plots ####
F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "Natural Light OCC")
F2_info <- plot(F2_fit, type = "infoSE", main = "F2")
F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = "F2")

## F3 Plots ####
F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "Smart Device OCC")
F3_info <- plot(F3_fit, type = "infoSE", main = "F3")
F3_iteminfo <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, main = "F3")

## F4 Plots ####
F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "Sleep Environment OCC")
F4_info <- plot(F4_fit, type = "infoSE", main = "F4")
F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "F4",cex = .8)

## F5 Plots ####
F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "Electric Light OCC")
F5_info <- plot(F5_fit, type = "infoSE", main = "F5")
F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = "F5")

@@

```{r IRTreliability, include=F}
#conditional reliability
F1.reliability <- plot(F1_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )
F2.reliability <- plot(F2_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )
F3.reliability <- plot(F3_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )
F4.reliability <- plot(F4_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )
F5.reliability <- plot(F5_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )

##IRT reliability (marginal reliability of scales)
F1.marginal.rel <- marginal_rxx(F1_fit)
F2.marginal.rel <-marginal_rxx(F2_fit)
F3.marginal.rel <-marginal_rxx(F3_fit)
F4.marginal.rel <-marginal_rxx(F4_fit)
F5.marginal.rel <-marginal_rxx(F5_fit)

##Scale characteristic curve
F1.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
F2.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
F3.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
F4.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
F5.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
```

@@

```{r itmeinfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
          labels = "AUTO", label_size = 10,align = "v")

@@

```{r IRTscoreCor, results='asis'}
apa_table (theta.correlation.matrix, caption = "correlation coefficents of obtained scores and estimated latent trait for each factots", note = "* p < 0.05; ** p < 0.01; *** p < 0.001"  )
```
